When are Fuzzy Extractors Possible?

### 2014-10-05 info-bounds/FuzzyExtPossibility.tex
run through body of paper

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. 
The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.  Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.  
Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.  Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University. Work done in part while the author was at Boston University.  Email: {\tt asmith@psu.edu}.  }}
}
\begin{document}
\maketitle

\begin{abstract}
Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key. To help eliminate noise, they produce a non secret helper string. This helper value allows the key to be regenerated from a nearby point.  Known constructions of fuzzy extractors do not provide security for most noisy distributions that occur in practice.

The nonsecret helper string allows an adversary to learn the generated key if they can guess a point close to the original reading.  A necessary condition to derive keys from a distribution is that no adversary can guess nearby points.  We call this condition \emph{fuzzy min-entropy}.  In the interactive setting, fuzzy min-entropy is both a necessary and sufficient condition for security.  In this work, we ask whether fuzzy min-entropy is a sufficient condition for security in the fuzzy extractor setting.

A key impediment to providing security is distributional uncertainty.  We consider two settings, first where the fuzzy extractor knows the precise distribution and second the fuzzy extractor knows the distribution comes from some family.  We show that fuzzy min-entropy is a sufficient condition in the first setting and insufficient in the second setting.  That is, there is families of distributions with fuzzy min-entropy that no fuzzy extractor can derive keys from.  Our results are information-theoretic.

\bnote{keep editing}
\end{abstract}

@@

The security requirement for fuzzy extractors that is $\key$ uniform even to a (computationally unbounded) adversary who has observed $p$.   This requirement is  harder to satisfy as the allowed error tolerance $t$ increases, because it becomes easier for the adversary to guess $\key$ by guessing a $w'$ within distance $t$ of $w$ and running $\rep(w',p)$.

@@

superlogarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(we show this in \propref{prop:fuzz necessary}, which formalizes the above intuition). 
However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.

\paragraph{Tight Characterization for the Case of a Known Distribution}
We show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}). We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.  It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).

@@

We show comparable, but stronger, results for secure sketches.  Namely, we show in \thref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known. (In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by applying a randomness extractor.) On the other hand, there is a family of sources with superlogarithmic $\Hfuzz(W)=\Hoo(W)$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}). The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).

@@

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz(W)$.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ''levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.  We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.

\paragraph{Techniques for Negative Results for Distribution Families}
Note constructing a family of distributions $\mathcal{W}$ and proving impossibility for a uniformly random (rather than worst-case) $W\in \mathcal{W}$  is sufficient.
We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
the adversary knows $W$.   To exploit the asymmetry, we construct $\mathcal{W}$ so that conditioning on the knowledge of $W$ reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on the entire space.

Then we show how the adversary can exploit the knowledge of the affine line to reduce the uncertainty about $w$ (in the secure sketch case) or $\key$ (in the fuzzy extractor case). 
In the secure sketch case, $\sketch$ can be used to find fixed points of $\rec(\cdot, \sketch)$ which, by the correctness requirement of the sketch, must be separated by minimum distance $t$. This means there aren't too many of them, so few can lie on an average line, permitting the adversary to guess one easily.

@@

The result for fuzzy extractors is delicate.  The fact that $p$ partitions the space~(into non overlapping regions) relies on perfect correctness.  Extending this result to imperfect correctness seems challenging and is an interesting open problem.
The result also relies on the majority of points lying near boundaries of a set. Indeed, fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}

\subsection{Sufficiency of $\Hfuzz(W)$ in related settings}
\label{sec:related settings}
We have evidence that fuzzy min-entropy is sufficient in settings related to information-theoretic fuzzy extractors.  
%We first consider the interactive setting.  
First, an alternate definition fuzzy extractors and secure sketches may provide computational security instead of information-theoretical security~\cite{fuller2013computational}.  In this setting, under the strong assumption of semantically-secure multilinear maps, fuzzy extractors and secure sketches can be constructed for any distribution $W$~\cite{BitanskyCKP14}.  We note that the secure sketch of~\cite{BitanskyCKP14} provides computational unpredictability of $W |p$.  Our negative result that implies that $W|p$ cannot have pseudoentropy~(discussion in \secref{sec:feas comp sec sketch}).

@@

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:distribution aware}, we construct a distribution-aware fuzzy extractor for all distributions with fuzzy min-entropy.  In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.

\section{Preliminaries}
\label{sec:preliminaries}
%For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$. % For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$. 
 Unless otherwise noted logarithms are base $2$.
Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.

The {\em min-entropy} of $W$ is $\Hoo(W) = -\log(\max_w \Pr[W=w])$,
and the {\em average (conditional)} min-entropy of $W$ given $P$ is  $\Hav(W|P) = -\log(\expe_{p\in P} \max_{w} \Pr[W=w|P=p])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   Let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
%\begin{definition}[Conditional Hartley Entropy]
%\label{def:conditional hartley}
The conditional Hartley entropy of $W |P $ is $\tilde{H}_0(W |P) = \log ( \expe_{p\in P} |\{w | \Pr[W=w |P=p]>0\}|)$.
%\end{definition}

@@

In this section, we define fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with modifications.  First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Second, in the \emph{distribution-oblivious} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
%\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
%This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  
We discuss distribution-aware algorithms in \secref{sec:distribution aware def}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

@@

\noindent
Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.  The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that minimally decreases the entropy of $w$, while mapping nearby $w'$ to $w$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.  \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.  \rec takes an element $w'\in\mathcal{M}$ and $ss\in\{0,1\}^*$.  $(\sketch, \rec)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}

\noindent In the above definitions, the errors are chosen before $ss$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$),  there is no correctness guarantee.  
A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}:

@@

In an ideal world, we could provide a reproduce functionality as an oracle.  In this world, the key is output if a close point is provided, and no response is provided otherwise.  We call the performance of an adversary in this ideal world fuzzy min-entropy:

\begin{definition}
\label{def:fuzzy min-ent}
The $t$-fuzzy min-entropy of a distribution $W$ in a metric space $(\mathcal{M}, \dis)$ is:
\[
\Hfuzz(W) = -\log \left(\max_{w'}  \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)
\]
\end{definition}

Fuzzy min-entropy is a necessary condition for security~(proof in \apref{sec:proof fuzz necessary}):%If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).  We make this intuition formal:
%For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{proposition}
\label{prop:fuzz necessary}
Let $W$ be a distribution over $(\mathcal{M}, \dis)$ and let $n= \log |\mathcal{M}|$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
 with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
\end{proposition}

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
\noindent
There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy.  We now describe distribution-aware algorithms.

\subsection{Distribution-aware algorithms}
\label{sec:distribution aware def}
%To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.  
We call an algorithm with complete information on the distribution $W$ \emph{distribution-aware}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):

\begin{definition}
Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness:} 
$
\forall w\in W$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
Correctness is guaranteed only for the support of $W$.
\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.  We assume distribution-aware algorithms are \emph{inefficient}.  Finding a natural model of specifying distributions that allows for efficient~(yet generic) distribution-aware constructions of sketches and extractors is an interesting problem.

\section{Sufficiency of $\Hfuzz(W)$ for Distribution-Aware Algorithms}
\label{sec:distribution aware}
In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
We first consider flat distributions and show that hashing maintains fuzzy min-entropy and suffices to disambiguate points.  We then turn to arbitrary distributions.

%The summary of our results is in Table~\ref{tab:upper bounds}.

%\begin{table}
%\begin{centering}
%\begin{tabular}{l | l}
%Class of Distribution & Residual entropy achieved by construction\\
%\hline
%Well-spread distribution & $\Hfuzz(W)$ \\
%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ \\
%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$
%\end{tabular}
%\caption{Residual entropy of distribution-aware secure sketches from \secref{sec:distribution aware}.    Here $\delta$ denotes the probability of incorrect reconstruction and $\mathcal{M}$ is the metric space.  Recall that $\Hfuzz(W)$ is an upper bound for the residual entropy.}
%\label{tab:upper bounds}
%\end{centering}
%\end{table}
%\bnote{I'm not convinced this table is useful}
%We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).  We then show that building distribution-agnostic secure sketches and fuzzy extractors is significantly harder.

>>>>

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{
Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston University and MIT Lincoln Laboratory. The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.  Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.}  \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.} \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.  Pennsylvania State University; work performed while at Boston University's Hariri Institute for Computing and RISCS Center, and Harvard University's
``Privacy Tools'' project.}}
}
\begin{document}
\maketitle

\begin{abstract}
Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key. To help eliminate noise, they produce a non secret helper string. This helper value allows the key to be regenerated from a nearby point.

The nonsecret helper string allows an adversary to learn the generated key if they can guess a point nearby to the original reading.  A necessary condition for key derivation is hardness of guessing nearby points.  We call the maximum probability mass of nearby points \emph{fuzzy min-entropy}.  Many practical sources have no known construction of fuzzy extractors but have fuzzy min-entropy.  There is evidence fuzzy min-entropy is sufficient to construct computational fuzzy extractors.\bnote{how to work in the interactive case?}
In this work, we ask: \emph{is fuzzy min-entropy sufficient to build an information-theoretic fuzzy extractor?}

We first consider a setting where the fuzzy extractor knows the precise distribution of the physical source.  In this setting, we construct a fuzzy extractor for any distribution with fuzzy min-entropy.

However, high-entropy distributions can never be fully observed and must be modeled. It is imprudent to assume that the designer's model of a distribution is completely accurate---the adversary may have a better model.  Thus, fuzzy extractors are normally built for families of distributions.  This uncertainty is an impediment to security.  We show a family of distributions such that no fuzzy extractor can extract a single key bit out for an average member of the family.

\bnote{mention secure sketches?}
\bnote{keep editing}
\bnote{nearby or close?  be consistent}
\bnote{I renamed section titles to get rid of distribution aware and oblivious.  don't quite like them}
\end{abstract}

@@

The security requirement for fuzzy extractors is that $\key$ is uniform even to a (computationally unbounded) adversary who has observed $p$.   This requirement is  harder to satisfy as the allowed error tolerance $t$ increases, because it becomes easier for the adversary to guess $\key$ by guessing a $w'$ within distance $t$ of $w$ and running $\rep(w',p)$.

@@

Superlogarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition). 
However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.

\paragraph{Tight Characterization for the Case of a Known Distribution}
We show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}). We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a \emph{known distribution} $W$.  It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).

@@

We show comparable, but stronger, results for secure sketches.  Namely, we show in \thref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known. (In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by applying a randomness extractor.) \bnote{should be citing same thing for sketch and fuzzy extractor.  its the same corollary}

On the other hand, there is a family of sources with superlogarithmic $\Hfuzz(W)=\Hoo(W)$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}). The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).

@@

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz(W)$.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ``levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.  We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.

\paragraph{Techniques for Negative Results for Distribution Families}
We construct a family of distributions $\mathcal{W}$ and prove impossibility for a uniformly random $W\in \mathcal{W}$~(instead of proving impossibility for a worst-case $W$).
We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
the adversary knows $W$.   To exploit the asymmetry, we construct $\mathcal{W}$ so that conditioning on the knowledge of $W$ reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on the entire space. \bnote{this isn't quite accurate, the first coordinate is known.  you have no info on the rest of the support}

Then we show how the adversary can exploit the knowledge of the affine line to reduce the uncertainty about $w$ (in the secure sketch case) or $\key$ (in the fuzzy extractor case). 
In the secure sketch case, $ss$ can be used to find fixed points of $\rec(\cdot, ss)$ which, by the correctness requirement of the sketch, must be separated by minimum distance $t$. This means there aren't too many of them, so few can lie on an average line, permitting the adversary to guess one easily.

@@

The result for fuzzy extractors is delicate.  The fact that $p$ partitions the space~(into non overlapping regions) relies on perfect correctness.  Extending this result to imperfect correctness seems challenging and is an interesting open problem.
The result also relies on the majority of points lying near boundaries of a set. Indeed, fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set is not the majority of its area.\bnote{cite cite cite!!!}

\subsection{Sufficiency of $\Hfuzz(W)$ in related settings}
\label{sec:related settings}
\bnote{this needs work}
We have evidence that fuzzy min-entropy is sufficient in settings related to information-theoretic fuzzy extractors.  
%We first consider the interactive setting.  
First, an alternate definition fuzzy extractors and secure sketches may provide computational security instead of information-theoretical security~\cite{fuller2013computational}.  In this setting, under the strong assumption of semantically-secure multilinear maps, fuzzy extractors and secure sketches can be constructed for any distribution $W$~\cite{BitanskyCKP14}.  We note that the secure sketch of~\cite{BitanskyCKP14} provides computational unpredictability of $W |p$.  Our negative result that implies that $W|p$ cannot have pseudoentropy~(discussion in \secref{sec:feas comp sec sketch}).

@@

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:known distributions}, we construct a fuzzy extractor for every known distribution with fuzzy min-entropy.  In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we provide negative results for secure sketches and fuzzy extractors for families of distributions respectively.

\section{Preliminaries}
\label{sec:preliminaries}
%For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$. % For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$. 
Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.
 Unless otherwise noted logarithms are base $2$.
The {\em min-entropy} of $W$ is $\Hoo(W) = -\log(\max_w \Pr[W=w])$,
and the {\em average (conditional)} min-entropy of $W$ given $P$ is  $\Hav(W|P) = -\log(\expe_{p\in P} \max_{w} \Pr[W=w|P=p])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   Let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
the conditional Hartley entropy of $W |P $ is $\tilde{H}_0(W |P) = \log ( \expe_{p\in P} |\{w | \Pr[W=w |P=p]>0\}|)$.

@@

In this section, we define fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with modifications.  First we allow for error, as discussed in \cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}.  Second, in the \emph{family of distributions} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
%\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
%This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  
We discuss known distribution algorithms in \secref{sec:known distributions def}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

@@

\noindent
Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.  The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness}) and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that minimally decreases the entropy of $w$, while mapping nearby $w'$ to $w$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.  \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.  \rec takes an element $w'\in\mathcal{M}$ and $ss\in\{0,1\}^*$.  $(\sketch, \rec)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}$ if $\dis(w,w')\leq t$ then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}

\noindent In the above definitions, the errors are chosen before $ss$ (resp., $p$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$),  there is no correctness guarantee.  
A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}:

@@

In an ideal world, $p$ is not useful to an adversary.  The adversary's only attack method is to execute $\rep(\cdot, p)$ on different $w'$.  In this world, $\rep$ outputs $\key$ if the input is close enough and provides no other  information.  The security of a fuzzy extractor in this world is the maximum weight of $W$ inside a ball of radius $t$:

\begin{definition}
\label{def:fuzzy min-ent}
The $t$-fuzzy min-entropy of a distribution $W$ in a metric space $(\mathcal{M}, \dis)$ is:
\[
\Hfuzz(W) = -\log \left(\max_{w'}  \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)
\]
\end{definition}
\noindent
Fuzzy min-entropy is a necessary condition for security~(proof in \apref{sec:proof fuzz necessary}):
\begin{proposition}
\label{prop:fuzz necessary}
Let $W$ be a distribution over $(\mathcal{M}, \dis)$ and let $n= \log |\mathcal{M}|$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
 with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
\end{proposition}

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
\noindent
There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy.  We now describe the known distribution setting.

\subsection{Known Distribution Algorithms}
\label{sec:known distributions def}
%To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.  
We call an algorithm with complete information on $W$ \emph{known distribution}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):

\begin{definition}
Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{known distribution secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness:} 
$
\forall w\in W$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
Correctness is guaranteed only for the support of $W$.
\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.  We assume known distribution algorithms are \emph{inefficient}.  Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.

\section{Sufficiency of $\Hfuzz(W)$ for Known Distribution Algorithms}
\label{sec:known distributions}
In this section, we show it is possible to build known distribution secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
We first consider flat distributions and show that hashing maintains fuzzy min-entropy and suffices to disambiguate points.  We then turn to arbitrary distributions.
%\subsection{Well-Spread Distributions}
%\bnote{can remove this section if we need space}
%We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.  Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.  Error-correction is ``easy'' when all points of $W$ are far apart.  Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points.  %Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).  However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.  
%We begin by defining a well-spread distribution.
%
%\begin{definition}
%A distribution $W$ is called \emph{$t_{cor}$-well spread} if for all $w, x\in W, \dis(w, x)\ge t_{cor}$.
%\end{definition}
%Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has superlogarithmic min-entropy).  Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.\footnote{This result is intuitive.  However, our negative results for the family of distributions setting will be for families of well-spread distributions.  This result illustrates how different the known distribution and family of distributions settings are.}
%\begin{lemma}
%\label{lem:nosketchwellspread}
%Let $W$ be a $t_{cor}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, W, m, \lfloor( t_{cor}-1)/2\rfloor)$-secure sketch with no error that works for $W$.  In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.  \rec is efficient if there exists efficient decoding for the points in $W$.  By \lemref{lem:fuzzy ext construction} there also exists a $(\mathcal{M}, W,m -2\log 1/\epsilon, \lfloor (t_{cor}-1)/2\rfloor, \epsilon)$-fuzzy extractor with no error.
%\end{lemma}  
%\begin{proof}
%It suffices to show that for any $w'$ there exists a unique $w\in W$ such that $\dis (w, w')\le \lfloor (t_{cor}-1)/2\rfloor$.  Since $W$ is $t_{cor}$-well spread, for all $w_0, w_1 \in W, \dis (w_0, w_1)\ge t_{cor}$.  Then by the triangle inequality,
%\[
%t_{cor}\ge \dis(w_0, w_1) \ge \dis(w_0, w') + \dis(w', w_1).\]
%This is only true if at least one of $\dis(w_0, w')$ or $\dis(w', w_1)$ is greater than $\lfloor (t_{cor}-1)/2\rfloor$.
%\end{proof}

\subsection{Secure Sketches for Flat distributions}
A distribution is flat if all points in its support have the same probability:
\begin{definition}
A distribution $W$ is \emph{flat} if for all $w_0, w_1 \in W$, $\Pr[W=w_0] = \Pr[W=w_1]$.  
\end{definition}

Fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme.  We denote the ball with the largest number of points as $B_{t, max}$.  Fuzzy min-entropy is the weight of the maximum probability ball~(\defref{def:fuzzy min-ent}).  For flat distributions, this is proportional to the largest number of points in any ball.  More precisely, 
\begin{align}
\Hfuzz(W) &= -\log \left(\max_{w^* \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w^*)\le t\} \right|* \Pr[W=w]\right) \nonumber \\
&= -\log\left( \max_{w^* \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w^*)\le t\}| *2^{-\Hoo(W)}\right) \nonumber \\
&=\Hoo(W) -\log\left( \max_{w^* \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w^*)\le t\} |\right)\nonumber \\
&= \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
\end{align}
